\section{Online API documentation}\label{online-api-documentation}

\begin{quote}
The junior developer read books and tutorials; The senior developers
read the API documentation; Only the platform developers and library
writers read the standards and specs.
\end{quote}

Why I should investigate into this part? The reason is simple: we want
to know \emph{how developer learns about the APIs and its intended
usage}.

Thus, we should pay attention to the following several things:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  How does the single interface documentation look like?
\item
  Can developer find the usage of some particular functionality quick?
\item
  Is there enough but concise examples along side?
\item
  How is the edge cases and correctness issues mentioned?
\item
  How is the compatibility, security and performance issues mentioned?
\end{enumerate}

\subsection{Sources}\label{sources}

I found the MDN and MSDN have detailed API docs:

\begin{itemize}
\tightlist
\item
  \href{https://developer.mozilla.org/en-US/docs/Web/API/WebGL_API}{Mozilla
  Developer Network}
\item
  \href{https://msdn.microsoft.com/en-us/library/dn621085(v=vs.85).aspx}{Microsoft
  Developer Network}
\end{itemize}

On the contrary, I don't find API doc about WebGL on
\href{https://www.chromium.org/developers}{Chromium's online
documentation};

\href{http://dev.opera.com}{Dev.Opera} has a lot of tutorials but not
API docs.

I find nothing significant on \href{https://developer.apple.com}{Apple
Developer site} either.

\subsection{Interface structure}\label{interface-structure}

\subsubsection{MDN}\label{mdn}

For example,
\href{https://developer.mozilla.org/en-US/docs/Web/API/WebGLRenderingContext/copyTexImage2D}{copyTexImage2D}

There are short induction, syntax, parameters and return value
(semantics, types, ranges), examples, specification, browser
compatibility, related interfaces.

\subsubsection{MSDN}\label{msdn}

Same example,
\href{https://msdn.microsoft.com/en-us/library/dn302380(v=vs.85).aspx}{copyTexImage2D}

Short intro, syntax, parameters and return value (semantics, more
explicit types, ranges), remarks, WebGL errors, related interfaces

\subsection{Usability}\label{usability}

The navigation of MDN is better than MSDN. And most of time the Google
will return MDN on searching a particular interface.

Also, the MDN provides per-interface examples and a lot of tutorials;
MSDN is short at this.

\subsection{Edge cases and
correctness}\label{edge-cases-and-correctness}

Both consider edge cases and special values. The MSDN has a WebGL errors
documentation, so it is more explicit about correctness.

\subsection{Compatibility, security and
performance}\label{compatibility-security-and-performance}

\subsubsection{MDN}\label{mdn-1}

\begin{itemize}
\tightlist
\item
  Compatibility: Information about conformity in all major desktop and
  mobile browsers.
\item
  Security: Not explicit
\item
  Performance: Not explicit
\end{itemize}

\subsubsection{MSDN}\label{msdn-1}

\begin{itemize}
\tightlist
\item
  Compatibility: Only one icon showing IE version supporting the
  interface.
\item
  Security: Not explicit
\item
  Performance: Not explicit
\end{itemize}
